Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-10 paper/uist_2016/paper.tex
added three more references in related work

\section{Related Work}
\subsection{Digital Memories}
Rewind is guided by literature about mediated memories, which provides a theoretical underpinning behind how the Rewind experience is constructed. \textit{Mediated Memories in the Digital Age} offers inspiration informing the relationship between experiences and memories \cite{van2007mediated}. van Dijck notes, ``Remembering is vital to our well being, because without autobiographical memories we would have no sense of past or future, and we would lack any sense of continuity'' (pg. 3). Rewind aims to give the user this sense of continuity in a time segment which has a past and future. By picking a start and end location from a particular trip and generating a Rewind between these points, the user relives their memories in a continuous manner.

@@

Other research has used location history not to create a new interface for the user, but for other applications. Neuhaus's UrbanDiary project \cite{neuhaus2010urbandiary} uses GPS devices to create and visualize ``personal tracks'' as well as collective tracks for a city. These personal tracks are created using data from time and location tracking for each trip by each individual. The researchers focused on comparing the different visualization techniques used to portray the data. A two-month study involved twenty participants wearing GPS devices, but as the paper was published in 2010, they did not use smartphone GPS data. Each participant wore a device, and the paper suggests that doing so helped them feel in charge of the data collection. Furthermore, GPS tracking is noted as a good method for collecting data about movement of each person. A further exploration of this project was what participants' perceptions were while moving. The data from this study shows each person's location data can be used as a unique fingerprint. This supports the idea that location data can be used to help people recreate their individual travel experiences, for purposes of reminiscing and even sharing. In a similar vein, Cranshaw et al. \cite{cranshaw2012livehoods} recognize the ability for collective location data to understand the social patterns in a city. That everyone travels their own path, and this is part of their identity, is a core theme in Rewind.

@@

\section{The Rewind System}
\textit{Rewind} recreats the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers. Differing from previously studied hyperlapse creation techniques by \cite{kopf2014firstperson, joshi2015realtime}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight. \textit{Rewind} inputs lifeloggers' geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images. The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues. \textit{Rewind} is a client-side only application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store it.

>>>>

\section{Related Work}
\subsection{Digital Memories}
Rewind is guided by literature about mediated memories, which provides a theoretical underpinning behind how the Rewind experience is constructed. \textit{Mediated Memories in the Digital Age} offers inspiration informing the relationship between experiences and memories \cite{van2007mediated}. van Dijck notes, ``Remembering is vital to our well being, because without autobiographical memories we would have no sense of past or future, and we would lack any sense of continuity'' (pg. 3). Rewind aims to give the user this sense of continuity in a time segment which has a past and future. By picking a start and end location from a particular trip and generating a Rewind between these points, the user relives their memories in a continuous manner. Similarly in his famous seminal paper \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access through``associative trails'', giving mankind the ability of``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''. Rewind in its most ambitious form, perhaps strives to become a potential counterpart of \textit{memex} for retrieving, and sharing of autobiographical memories of one’s sensory experiences about past visits.

@@

Another project by de Silva and Aizawa has also relied on geolocation data to provide a visual examination of interested traveling routes by linking geo-tagging metadata with online imageries, specifically Google Street View images \cite{deSilva:2009:RMT:1631272.1631414}. The authors proposed a sketch-based interface that would perform spatial and temporal queries on line drawings specified by the users. Rewind resembles this interactive system, in a way that the reconstructed sceneries are of a careful mapping results from GPS data and Google Street View images. However, Rewind differs in that the mapping is finalized with GPS data provided by lifeloggers tracked using smartphones. This means that Rewind serves more of a getaway for recalling episodic memory rather than reviewing a potential travelling itinerary, aiming to provide a mechanism for reminiscence and sharing of past experience while exploring lifeloggers' behavioral patterns. Moreover, the reconstruction techniques used in Rewind would differentiate the same retrieved image with various temporal cues such as changes in seasons; yet the immediate results from the temporal queries suggested by de Silva and Aizawa have not been fully revealed.

Other research has used location history not to create a new interface for the user, but for other applications. Neuhaus's UrbanDiary project \cite{neuhaus2010urbandiary} uses GPS devices to create and visualize ``personal tracks'' as well as collective tracks for a city. These personal tracks are created using data from time and location tracking for each trip by each individual. The researchers focused on comparing the different visualization techniques used to portray the data. A two-month study involved twenty participants wearing GPS devices, but as the paper was published in 2010, they did not use smartphone GPS data. Each participant wore a device, and the paper suggests that doing so helped them feel in charge of the data collection. Furthermore, GPS tracking is noted as a good method for collecting data about movement of each person. Using geotagged images from Flickr, Becker et al's work has shown that movement trajactories in metropolian areas tend to converge at Points of Interests(POIs) \cite{Becker2015}. As noted, a further exploration of these projects could be investigating what participants' perceptions were while moving. The data from these studies show each person's location data can be used as a unique fingerprint. This supports the idea that location data can be used to help people recreate their individual travel experiences, for purposes of reminiscing and even sharing. In a similar vein, Cranshaw et al. \cite{cranshaw2012livehoods} recognize the ability for collective location data to understand the social patterns in a city. That everyone travels their own path, and this is part of their identity, is a core theme in Rewind.

@@

\section{The Rewind System}
\textit{Rewind} recreats the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers. Differing from previously studied hyperlapse creation techniques by Kopft et al. and Joshi et al \cite{opf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight. \textit{Rewind} inputs lifeloggers' geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images. The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues. \textit{Rewind} is a client-side only application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store it.
